### 2019-08-05 thesis.tex
*** empty log message ***

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics. At the same time, observations of space plasma phenomena have
been gaining increasing relevance in the advance of theoretical\cite{YZKS16,
  Tigik2017b}, computational\cite{Donnert2014,Pezzi2018}, and experimental
\cite{Howes2018,Peterson2019} plasma physics research.

A recent example
of this complementarity is presented in Ref. \cite{Peterson2019}, where the
authors reproduced in the laboratory a magnetic structure called \emph{Parker spiral}, which is
related to the acceleration process of solar - and stellar - winds. The
authors compare their results with numerical simulation of the same
structure, since in situ observations of this particular phenomena are not
available yet. In Ref. \cite{Chen2019}, we have the opposite situation.

% Since the ubiquity of plasmas in space came as a fact, astrophysicists and
% plasma physicists have been noticing an increasing necessity for exchanging
% knowledge and mutually collaborating with their results. A particular field
% of research that has been acting for a long time as a bridge between these two
% areas is the solar physics. The accessibility of the solar plasma to direct,
% in situ measurements, highly resolved remote sensing and high-resolution
% spectroscopy turned the solar system into Earth's space physics laboratory.

>>>>

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics \cite{Alfven1950,Parker1956,Alfven1961,Gailitis1964}. At the
same time, the analysis and interpretation of observational data have been
gaining increasing relevance in the progress of theoretical, computational,
and experimental plasma physics research \cite{YZKS16,Donnert2014,Pezzi2018,
  Howes2018,Peterson2019}. This interconnection between plasma physics and
astrophysics was scrutinized by Hannes Alfvén, 1970's Nobel prize winner
plasma physicist, in a Physics Today's article \cite{Alfven1971} in 1971.

% Since the ubiquity of plasmas in space came as a fact, astrophysicists and
% plasma physicists have been noticing an increasing necessity for exchanging
% knowledge and mutually collaborating with their results. A particular field
% of research that has been acting for a long time as a bridge between these two
% areas is the solar physics. The accessibility of the solar plasma to direct,
% in siztu measurements, highly resolved remote sensing and high-resolution
% spectroscopy turned the solar system into Earth's space physics laboratory.
